Results

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected reasons for choice
corrected missing letters

### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->

@@

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```
Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, we reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: $$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

### Manipulation checks

@@

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
```
Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found online on OSF (<https://osf.io/vnj8x/>).

@@

Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
The starting point for this was the adapted MLM, which we have reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$ 
As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
